%-------------------------
% My resume in Latex
% Author : Diomidis Anadiotis
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{pgffor}
\usepackage{hyphenat}
\usepackage{fontawesome}
\usepackage{xcolor}
\usepackage{changepage}
\usepackage{geometry}
\input{glyphtounicode}
\usepackage{libertine}

%---------- FONT OPTIONS ----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Set margins to default
\usepackage{geometry}
\geometry{
  left=0.5in,   % Standard left margin
  right=0.5in,  % Standard right margin
  top=0.5in,    % Standard top margin
  bottom=1in, % Standard bottom margin
  headheight=14pt, % Standard header height
  includeheadfoot % Include space for header/footer
}
\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\titleformat{name=\section,numberless}[block]{\centering\scshape\large}{}{0em}{}
\newcommand{\centeredsection}[1]{\section*{\centering #1}}

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-1pt}}
  }
}

\newcommand{\resumeItemTight}[1]{
  \item\small{
    {#1 \vspace{-5pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{1mm}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{1mm}
}


\newcommand{\resumeEducationHeading}[6]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      \textit{\small#5} & \textit{\small #6} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeOrganizationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
      \textit{\small#3}
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeCenteredSection}[1]{
  \section*{\centerline{#1}}
  \vspace{-8pt}
}

\newcommand{\resumeItemColumns}[1]{
  \begin{tabularx}{\textwidth}{>{\centering\arraybackslash}X >{\centering\arraybackslash}X >{\centering\arraybackslash}X}
    #1
  \end{tabularx}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%---------- HEADING ----------

\begin{adjustwidth}{-0.2in}{-0.2in}
  \begin{center}
    {\textbf{\LARGE \scshape Diomidis Anadiotis}} \\ \vspace{3pt}
    \small
      \faMobile \hspace{.5pt} \href{tel:447518630975}{+44 075 1863 0975}
      $|$
      \faAt \hspace{.5pt} \href{mailto:info@diomidis.net}{info@diomidis.net}
      $|$
      \faLinkedinSquare \hspace{.5pt} \href{https://www.linkedin.com/in/diomidis-anadiotis/}{LinkedIn}
      $|$
      \faGithub \hspace{.5pt} \href{https://github.com/diomidis}{GitHub}
      $|$
      \faGlobe \hspace{.5pt} \href{https://diomidis.net}{diomidis.net}
      $|$
      \faMapMarker \hspace{.5pt} \href{}{E14 0LW, London}
  \end{center}
  \end{adjustwidth}
  

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

%-----------SUMMARY-----------------
\resumeCenteredSection{Summary}
\small{
  A methodical and well-organized London-based Senior Software Engineer with extensive experience in complex enterprise systems and technical leadership. Proven track record in full software development lifecycle including stakeholder management, system architecture, and leading development teams. Expert in C\#/.NET stack with specialization in scalable backend development, microservices architecture, and cloud-native solutions. Experienced in business analysis, requirements gathering, and translating business objectives into technical solutions. Strong background in DevOps practices, legacy system modernization, and mentoring junior developers. Seeking a senior engineering role that leverages technical expertise, leadership skills, and business acumen to deliver impactful solutions.
} \vspace{-5pt}

\resumeCenteredSection{Areas of Expertise}
\resumeItemColumns{
  Backend Development & System Architecture & Technical Leadership \\
  Microservices Design & Cloud Infrastructure & DevOps Practices \\
  C\# .NET Development & Database Design & API Integration \\
  Stakeholder Management & Team Mentoring & Agile Methodologies \\
  Azure \& AWS & Kubernetes \& Docker & Event-Driven Architecture
}

\resumeCenteredSection{Key Achievements}
\resumeItemListStart
    \resumeItemTight{Delivered mobile application launch in 2024 serving 221,000+ monthly active users with high availability and scalability}
    \resumeItemTight{Architected omni-channel service booking platform processing 220,000+ annual bookings via web and mobile applications}
    \resumeItemTight{Led OWA system implementation generating 360,000+ work approvals with 40\% approval rate, delivering £30M business value over 2 years}
    \resumeItemTight{Designed and implemented resource management system supporting 200+ branches across the country with integrated pricing matrix and recommendation engine}
    \resumeItemTight{Increased vehicle service work sales conversion rates to double-digit percentage year-over-year through system optimization and integration}
    \resumeItemListEnd
    
  
\resumeCenteredSection{Overview}
\resumeItemListStart
    \resumeItemTight{Extensive experience with microservices architecture, event-driven systems, and CQRS patterns in high-scale enterprise environments}
    \resumeItemTight{Proven technical leadership in cross-functional teams, mentoring junior developers and leading critical system implementations}
    \resumeItemTight{Strong background in cloud infrastructure (Azure, AWS), containerization (Kubernetes, Docker), and Infrastructure as Code (Terraform)}
    \resumeItemTight{Expert in system integration with 3rd party vendors, API design, and enterprise-scale application deployment and monitoring}
    \resumeItemTight{Demonstrated ability to translate complex business requirements into scalable technical solutions while maintaining high code quality standards}
    \resumeItemListEnd


%----------- WORK EXPERIENCE -----------
%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
  
    \resumeSubheading
      {\href{https://www.arnoldclark.com/about-us}{Arnold Clark}}{Glasgow, UK - Remote}
      {Software Engineer}{Dec 2021 - Present}
      \resumeItemListStart
        \resumeItem{}
        {Architected and delivered customer-facing applications serving hundreds of thousands of users for Europe's largest independent automotive company. Led full-stack development from inception to MVP release on business-critical enterprise systems, including mobile application launch achieving 221k monthly active users and omni-channel service booking platform processing 220k+ annual bookings.
        }
        \resumeItem{}
        {Designed and implemented microservices architecture following CQRS and event sourcing patterns, participating in monolith-to-microservices migration. Collaborated with cross-functional teams to ensure appropriate engineering decisions factoring in technical debt, systems design approaches, stability, monitoring, and business needs. Led resolution of critical production incidents and system outages.
        }
        \resumeItem{}
          {Mentored junior developers and placement students through technical guidance, code reviews, and knowledge sharing sessions. Authored comprehensive technical documentation and conducted 'lunch and learn' demonstrations. Built team capability through hands-on training in modern development practices and enterprise patterns.}
          \resumeItem{}
           {Owned complete workstreams across projects, overseeing junior developers and coordinating deliverables on tight deadlines. Managed go-live projects by liaising with customers and stakeholders, providing rapid troubleshooting and solution delivery. Contributed to key business metrics by boosting vehicle service sales conversion rates to double-digit percentage year-over-year.}
          \resumeItem{}
           {Integrated with 3rd party vendors and internal systems to deliver seamless omni-channel experiences. Implemented Infrastructure as Code (Terraform) for on-premises and cloud deployments. Developed integration solutions providing technicians access to vehicle-specific data including wiring diagrams and engine schematics.}
          \resumeItemListEnd
          \vspace{3mm}
    \resumeSubSubheading
     {Associate Software Engineer (Hybrid)}{Dec 2019 - Dec 2021}
     \resumeItemListStart
       \resumeItem{}
        {Developed multiple features for large-scale internal and public-facing systems, writing clean, SOLID-principles oriented, and well-tested code. Created new APIs, enhanced existing functionality, and maintained legacy systems while ensuring high code quality and comprehensive documentation.}
        \resumeItem{}
        {Collaborated effectively across departments including service desk, product teams, database reliability engineers, platform engineering, finance, marketing, and 3rd party vendors. Represented technical team in stakeholder meetings and translated business requirements into technical specifications.}
        \resumeItemListEnd
        \resumeSubSubheading
     {Systems Analyst (On Site)}{Dec 2017 - Dec 2019}
     \resumeItemListStart
        \resumeItem{}
          {Analyzed and evaluated business processes and systems as part of Aftersales business support team. Translated business requirements into detailed technical specifications, assessed system capabilities, identified improvements, and proposed technical solutions aligned with business goals.}
          \resumeItem{}
          {Coordinated between business stakeholders and IT development teams to ensure proposed solutions were technically feasible and business-aligned. Worked closely with Digital development teams, project managers, and IT stakeholders to troubleshoot issues and optimize system performance.}
     \resumeItemListEnd
     \vspace{3mm}

    \resumeSubheading
      {City Unity College}{Athens, Greece}
      {Research Assistant in Cognitive Computing/Computational Psychology}{Jan 2015 - Sep 2015}
      \resumeItemListStart
      \resumeItem{}
      {Developed cognitive research software focusing on the Euclidean Travelling Salesman Problem utilizing Eyetribe eye tracker for real-time cognitive process capture. Conducted selective attention experiments and analyzed data using R and RStudio, creating visualizations and models for cognitive insights in interdisciplinary research environment.}
      \resumeItemListEnd
      \vspace{3mm}

    \resumeSubSubheading
      {IT Systems Engineer}{Feb 2012 - Jan 2015}
      \resumeItemListStart
      \resumeItem{}
      {Managed network infrastructure and administered Windows/Linux servers and MSSQL Server environments. Automated educational course live streaming and recording using PowerShell and Bash scripting. Developed comprehensive backup and recovery documentation supporting compliance audits.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education \& Certifications}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Glasgow}{Glasgow, UK}
      {Master of Science in Information Technology (PgCert)}{Sep. 2016--Sep. 2017}
      \small{Relevant modules include advanced programming, databases, software engineering, systems and networks, software project management, algorithms, data structures and cyber security}
    \resumeSubheading
      {City University of Seattle}{Seattle, USA}
      {Bachelor of Science in Information Systems (ABET Accredited)}{Sept. 2011--June 2016}
      \small{Relevant modules include computer science, statistical computing, network communications, operating systems, web design and cloud computing, data analytics and IT compliance}
  \resumeSubHeadingListEnd

%--------TECHNICAL SKILLS------------
\section{Technical Skills}
  \resumeSubHeadingListStart
    \resumeItem{
      \textbf{Languages}{: C\#, JavaScript (ES6), TypeScript, HCL (Terraform), Groovy (Jenkins), HTML, CSS, T-SQL, PowerShell, Bash} \\[1mm]
      \textbf{Frameworks \& Libraries}{: .NET Core, ASP.NET, Entity Framework Core, React.js, Gatsby, RESTful APIs, GraphQL} \\[1mm]
      \textbf{Cloud \& DevOps}{: Azure (Functions, Service Bus, DevOps), AWS (Lambda, S3, EKS), Kubernetes, Docker, Terraform, Infrastructure as Code} \\[1mm]
      \textbf{Architecture \& Design}{: Microservices, Event-Driven Architecture, CQRS, Event Sourcing, Domain-Driven Design, SOLID Principles} \\[1mm]
      \textbf{Databases}{: MS SQL Server, Redis, CosmosDB, RavenDB, Event Store, NoSQL databases} \\[1mm]
      \textbf{Integration \& Messaging}{: Azure Service Bus, RabbitMQ, Kafka, REST APIs, OAuth2, JWT, SAML} \\[1mm]
      \textbf{Testing \& Quality}{: NUnit, Cypress, Newman, TDD, Integration Testing, End-to-End Testing, Performance Testing} \\[1mm]
      \textbf{Monitoring \& Observability}{: New Relic, Elasticsearch, Application Performance Monitoring, Logging, Alerting} \\[1mm]
      \textbf{Project Management}{: Agile Methodologies, Scrum, Stakeholder Management, Technical Leadership, Mentoring}\\[1mm]
    }
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}