%-------------------------
% My resume in Latex
% Author : Diomidis Anadiotis
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{pgffor}
\usepackage{hyphenat}
\usepackage{fontawesome}
\usepackage{xcolor}
\usepackage{changepage}
\usepackage{geometry}
\usepackage{ragged2e}
\input{glyphtounicode}
\usepackage{libertine}

%---------- FONT OPTIONS ----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Set margins to default
\usepackage{geometry}
\geometry{
left=0.5in, % Standard left margin
right=0.5in, % Standard right margin
top=0.5in, % Standard top margin
bottom=1in, % Standard bottom margin
headheight=14pt, % Standard header height
includeheadfoot % Include space for header/footer
}
\urlstyle{same}

\raggedbottom
% Remove \raggedright for better justification
\setlength{\tabcolsep}{0in}

% Better hyphenation and justification
\tolerance=1
\emergencystretch=\maxdimen
\hyphenpenalty=10000
\hbadness=10000

% Define custom colors
\definecolor{sectioncolor}{HTML}{005b96} % Deep blue for headings
\definecolor{namecolor}{HTML}{005b96} % Deep blue for name
\definecolor{textcolor}{HTML}{2c3e50} % Dark slate blue for main text

% Set default text color
\color{textcolor}

% Sections formatting
\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large\color{sectioncolor}
}{}{0em}{}[\color{sectioncolor}\titlerule \vspace{-5pt}]

\titleformat{name=\section,numberless}[block]{\centering\scshape\large\color{sectioncolor}}{}{0em}{}
\newcommand{\centeredsection}[1]{\section*{\centering \color{sectioncolor}#1}}

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
\item\small{
\justifying{#1} \vspace{-1pt}
}
}

\newcommand{\resumeItemTight}[1]{
\item\small{
\justifying{#1} \vspace{-5pt}
}
}

\newcommand{\resumeSubheading}[4]{
\item
\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
\textbf{#1} & #2 \\
\textit{\small#3} & \textit{\small #4} \\
\end{tabular*}\vspace{1mm}
}

\newcommand{\resumeSubSubheading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\textit{\small#1} & \textit{\small #2} \\
\end{tabular*}\vspace{1mm}
}


\newcommand{\resumeEducationHeading}[6]{
\vspace{-2pt}\item
\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
\textbf{#1} & #2 \\
\textit{\small#3} & \textit{\small #4} \\
\textit{\small#5} & \textit{\small #6} \\
\end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeProjectHeading}[2]{
\vspace{-2pt}\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\small#1 & #2 \\
\end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeOrganizationHeading}[4]{
\vspace{-2pt}\item
\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
\textbf{#1} & \textit{\small #2} \\
\textit{\small#3}
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeCenteredSection}[1]{
\section*{\centerline{#1}}
\vspace{-8pt}
}

\newcommand{\resumeItemColumns}[1]{
\begin{tabularx}{\textwidth}{>{\centering\arraybackslash}X >{\centering\arraybackslash}X >{\centering\arraybackslash}X}
#1
\end{tabularx}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%% RESUME STARTS HERE %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%---------- HEADING ----------

\begin{adjustwidth}{-0.2in}{-0.2in}
\begin{center}
{\textbf{\LARGE \scshape \color{namecolor}Diomidis Anadiotis}} \\ \vspace{3pt}
\small
\faMobile \hspace{.5pt} \href{tel:447518630975}{+44 075 1863 0975}
\(|\)
\faAt \hspace{.5pt} \href{mailto:info@diomidis.net}{info@diomidis.net}
\(|\)
\faLinkedinSquare \hspace{.5pt} \href{https://www.linkedin.com/in/diomidis-anadiotis/}{LinkedIn}
\(|\)
\faGithub \hspace{.5pt} \href{https://github.com/diomidis}{GitHub}
\(|\)
\faGlobe \hspace{.5pt} \href{https://diomidis.net}{diomidis.net}
\(|\)
\faMapMarker \hspace{.5pt} \href{}{E14 0LW, London}
\end{center}
\end{adjustwidth}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

%-----------SUMMARY-----------------
\resumeCenteredSection{Professional Summary}
\small{
\justifying
Customer-focused software engineer with proven expertise in technical initiatives to deliver robust, scalable and maintainable enterprise systems at Europe's largest independent automotive company. Specialised in architecting event-driven microservices using C\#/.NET Core, CQRS patterns, and Azure cloud technologies.
Demonstrated success in co-leading cross functional team efforts and mentoring engineers with excellent interpersonal and communication skills while delivering high-quality software at scale-managing complex product catalogs.
Strong background in building omnichannel fullstack customer experiences.
Experience includes legacy systems modernisation into modern cloud-native architectures while maintaining availability for mission-critical customer, internal and integration applications.
}

\resumeCenteredSection{Technical Expertise}
\resumeItemColumns{
.NET \& .NET Framework & CQRS with MediatR & React.js/TypeScript \\
Azure Service Bus & Docker/Kubernetes & TDD/Cypress Testing \\
Event-Driven Microservices & SQL Server/Redis & MassTransit Messaging \\
Domain-Driven Design & RESTful APIs/GraphQL & Data Analysis \& Interpretation
}

%----------- WORK EXPERIENCE -----------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{\href{https://www.arnoldclark.com/about-us}{Arnold Clark}}{London, UK --Remote}
{Senior Software Engineer}{Jan 2025--Now}
\resumeItemListStart
\resumeItem{
Co-led complete modernisation of customer-facing booking platform serving 220k monthly active users that improved customer journey conversion by 17\%, directly contributing to £15M+ in annual digital revenue growth.
}
\resumeItem{
Complete ownership of availability feature showing real-time appointment slots based on product catalog availability, reducing customer friction by 35-50\% (page bounces) and increasing bookings by 18.5\% (3k additional bookings in 6 weeks). Improved conversion rate by a further 7\% through data-driven UX optimization, eliminating multi-step navigation frustration while maintaining sub-second response times at scale.
}
\resumeItem{
Designed and implemented event-driven microservices using CQRS with MediatR, .NET Core 8, and Azure Service Bus, handling 50,000+ daily transactions with heavy background processing. Established distributed caching with Redis and implemented auto-scaling strategies in Kubernetes to handle peak loads.
}
\resumeItem{
Contributed heavily in real-time inventory synchronization system managing 10k products across 200+ locations, processing updates within milliseconds. Refactored legacy product and service branch availability engine with event-sourced (migrating from EventStore to Service Bus) ensuring accurate availability levels across web, mobile, and in-store channels.
}
\resumeItem{
Mentored junior engineers in SOLID principles, TDD practices, refactoring, green field development and cloud architecture patterns. Collaborated directly with product owners, UX designers, QA and business stakeholders.
}
\resumeItemListEnd
\vspace{3mm}
\resumeSubSubheading
{Software Engineer}{Dec 2021--Jan 2025}

\resumeItemListStart
\resumeItem{
Proposed, designed, and migrated third-party integration from resource-intensive database jobs to a high-performance event processing application, replacing legacy stored procedures and achieving 5x faster processing of millions of records while introducing comprehensive auditing capabilities; implemented using Hangfire for job scheduling, MassTransit for messaging, and a configuration-driven architecture supporting both direct database operations and service bus integration with enterprise-grade error handling and concurrent execution prevention}
\resumeItem{
Designed and developed RESTful APIs serving React frontends and internal department-wide applications, implementing layered architecture with clean separation of concerns; built reusable component libraries and maintained comprehensive API documentation using Swagger/OpenAPI specifications}
\resumeItem{
Designed and optimized SQL Server schemas and implemented persistence-based solutions for unstructured availability and product data types. Created efficient indexing strategies and query optimization reducing database response times by 60\% in some cases.
}
\resumeItemListEnd
\vspace{3mm}
\resumeSubSubheading
{Associate Software Engineer}{Dec 2019--Dec 2021}
\resumeItemListStart
\resumeItem{
Developed comprehensive test suites using NUnit and Cypress for end-to-end testing. Implemented automated testing strategies with TestContainers ensuring code quality across 20+ microservices and legacy codebases. Practiced test-first development approach from business requirements through to production code, whenever possible.
}
\resumeItem{
Worked closely with UX/UI teams, product managers, and business stakeholders to deliver small and medium-sized features. Dived into legacy codebases and located refactoring opportunities. Participated in regular Tech Development days, hackathons, and knowledge-sharing sessions to drive engineering excellence.
}
\resumeItemListEnd
\resumeSubSubheading
{Systems Analyst}{Dec 2017--Dec 2019}
\resumeItemListStart
\resumeItem{
Analyzed and modeled complex business domains, translating requirements into technical specifications. Worked with aftersales development team to understand product lifecycle management and customer journey optimization opportunities.
}
\resumeItemListEnd
\vspace{3mm}

\resumeSubheading
{City Unity College}{Athens, Greece}
{Research Assistant in Cognitive Computing}{Jan 2015--Sep 2015}
\resumeItemListStart
\resumeItem{
Developed cognitive research software focusing on the Euclidean Travelling Salesman Problem utilizing Eyetribe eye tracker
for real-time cognitive process capture. Conducted selective attention experiments and analyzed data using R and RStudio,
creating visualizations and models for cognitive insights in an interdisciplinary research environment.}
\resumeItemListEnd
\vspace{3mm}

\resumeSubSubheading
{IT Systems Engineer}{Feb 2012--Jan 2015}
\resumeItemListStart
\resumeItem{
Managed cloud infrastructure and automated deployment processes using PowerShell and Bash scripting. Administered Windows/Linux servers and SQL Server environments supporting high-availability applications.
}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{University of Glasgow}{Glasgow, UK}
{MSc in Information Technology}{Sep 2016--Sep 2017}
\small{\justifying Core modules: Advanced Programming, Software Engineering, Cloud Computing, Algorithms \& Data Structures, Agile Project Management}
\resumeSubheading
{City University of Seattle}{Seattle, USA}
{BSc in Information Systems - Systems Engineering (ABET Accredited)}{Sep 2011--Jun 2016}
\small{\justifying Relevant modules include computer science, statistical computing, network communications, operating systems, web design and
cloud computing, data analytics and IT compliance}
\resumeSubHeadingListEnd

\section{Technical Skills}
\resumeSubHeadingListStart
\resumeItem{
\textbf{Languages \& Backend Frameworks}{: C\#, .NET Core 6/8, .NET Framework, .NET Standard, R} \\[1mm]
\textbf{Frontend \& Web Technologies}{: React.js, TypeScript, JavaScript (ES6+), Redux, Next.js, HTML5, CSS3} \\[1mm]
\textbf{Architecture \& Design Patterns}{: Microservices, CQRS, Event Sourcing, Domain-Driven Design, Event-Driven Architecture} \\[1mm]
\textbf{Azure Cloud Services}{: Functions, Service Bus, App Services, Application Insights, DevOps Pipelines} \\[1mm]
\textbf{Data Storage}{: SQL Server, MySQL, RavenDB, EventStore, Redis, EF} \\[1mm]
\textbf{Messaging \& APIs}{: Azure Service Bus, MassTransit, RabbitMQ, Kafka, RESTful APIs, GraphQL, gRPC} \\[1mm]
\textbf{DevOps \& Infrastructure}{: Docker, Kubernetes, Terraform, CI/CD (Jenkins for on-prem, Azure DevOps), GitHub Actions} \\[1mm]
\textbf{Testing \& Quality Assurance}{: TDD, Unit/Integration Testing, Cypress, Performance Testing} \\[1mm]
\textbf{Monitoring \& Observability}{: New Relic, Application Insights, ELK Stack, Distributed Tracing} \\[1mm]
}
\resumeSubHeadingListEnd

%--------Volunteering------------
\section{Volunteering}
\resumeSubHeadingListStart
\resumeItem{
Served as openSUSE Project Advocate (2010-2014) promoting Linux distribution across Greece and Europe through translation, documentation, and bug fixing; volunteered at FOSDEM (2011-2014) and hosted Novell SUSE booth at LinuxCon Europe 2012 conference, contributing to open-source community engagement and technical evangelism}
\resumeSubHeadingListEnd

%-------------------------------------------
\end{document}